New lower bounds for Schur and weak Schur numbers

### 2021-04-08 article/intro.tex

>>>>

\qquad This paper offers new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
Rowley's "templates"-based approach for Ramsey numbers in 2020. Finding suitable templates allows us to apply Rowley's construction 
to get explicit partitions improving lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
the principle that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding
the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
5-subsets partition. The new lower bounds includes \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
